Bioverse: Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2024-11-20 src/tex/ms.tex
update discussion on FGK vs. M dwarfs

\subsection{An M~dwarf opportunity}
An interesting aspect lies in the distribution of host star properties, as different spectral types probe different past \gls{NUV} flux regimes.
FGK stars show a narrow distribution of maximum past \gls{NUV} fluxes in the \gls{HZ}, which may limit the diagnostic power of a survey depending on the (unknown) threshold \gls{NUV} flux.
With a pure FGK sample, a survey will be more sensitive to the low \gls{NUV} flux end of the hypothesis.
A lack of biosignatures on these planets would support the UV~Threshold Hypothesis.
Their presence would have little constraining power; it would either suggest that low NUV fluxes are sufficient for abiogenesis or indicate a different abiogenic pathway~\citep[e.g.,][]{Westall2018}.

On the other hand, M~dwarfs show a wider distribution of maximum past \gls{NUV} fluxes in their \glspl{HZ}.
While old M~dwarfs can be considered low-UV environments, a large fraction of them emit high \gls{NUV} fluxes into their \gls{HZ} during their early stages, in particular later subtypes~\citep{Richey-Yowell2023}.
An M~dwarf sample will thus help to test the high \gls{NUV} flux end of the UV Threshold Hypothesis; a higher occurrence of biosignatures here would support the hypothesis that a higher NUV flux is beneficial or necessary for life.
As our simulations show, the higher and more variable \gls{NUV} fluxes in M~dwarfs increase the likelihood of obtaining strong evidence for or against the hypothesis.
The combination of a lack of UV radiation today, which makes biosignature gases more detectable~\citep{Segura2005}, and a UV-rich past that may have enabled abiogenesis could make M~dwarfs the preferred targets for biosignature searches.

>>>>

\subsection{An M~dwarf opportunity}
An interesting aspect lies in the distribution of host star properties, as different spectral types probe different past \gls{NUV} flux regimes.
FGK stars show a narrow distribution of maximum past \gls{NUV} fluxes in the \gls{HZ}, which may -- depending on the (unknown) threshold \gls{NUV} flux -- limit the diagnostic power of a survey.
In the case of a pure FGK sample, it will essentially only be sensitive to \gls{NUV} flux thresholds $\sim \SIrange{200}{400}{\erg\per\second\per\centi\meter\squared}$, and the chance of detecting biosignatures diminishes rapidly for higher thresholds within this range (see Figure~\ref{fig:inhabited_aafo_nuv_thresh}).
Detected biosignatures in an FGK sample would have little constraining power on testing the UV~Threshold Hypothesis; they would either suggest that low NUV fluxes are sufficient for abiogenesis or indicate a different abiogenic pathway~\citep[e.g.,][]{Westall2018}.
A lack of biosignatures in a larger FGK sample would support the UV~Threshold Hypothesis.

On the other hand, M~dwarfs show a wider distribution of maximum past \gls{NUV} fluxes in their \glspl{HZ}.
While old M~dwarfs can be considered low-UV environments, a significant fraction of them emit high \gls{NUV} fluxes into their \gls{HZ} during their early stages, in particular later subtypes~\citep{Richey-Yowell2023}.
This will help to test the high \gls{NUV} flux end of the UV Threshold Hypothesis; a higher occurrence of biosignatures here would support the hypothesis that a higher NUV flux is beneficial or necessary for life.
At the same time, a fraction of host stars in our M~dwarf sample extends it to lower maximum past \gls{NUV} fluxes, enabling tests of the low \gls{NUV} flux end of the hypothesis.
The higher and more variable \gls{NUV} fluxes in M~dwarfs thus increase the likelihood of obtaining strong evidence for or against the UV~Threshold Hypothesis.
The combination of a lack of UV radiation today, which makes biosignature gases more detectable~\citep{Segura2005}, and a UV-rich past that may have enabled abiogenesis could make M~dwarfs the preferred targets for biosignature searches.
